koda: Deep Learning-Enhanced Pipeline for Keyword Detection in Document Images

### 2020-01-09 paper/paper.tex
Add matteo's part

\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=3cm]{geometry}

@@

@@

\begin{figure}[!htb]
	\includegraphics[width=\linewidth]{canny_gaussian.png}
	\caption{TODO}
	\label{fig:canny_gaussian}
\end{figure}

@@

\begin{figure}[htb!]
	\includegraphics[width=\linewidth]{canny_comparison.png}
	\caption{TODO}
	\label{fig:canny_comparison}
\end{figure}

@@

\begin{figure}[htb!]
	\centering
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{deep_edge_comparison.png}}%

@@

>>>>

\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage[margin=3cm]{geometry}

@@

\section{Architecture}

KODA architecture was inspired by a Dropbox article \footnote{https://blogs.dropbox.com/tech/2016/08/fast-and-accurate-document-detection-for-scanning/} which defines the steps to solve a problem similar to the one this project is based on.

The process is divided into two macro tasks (shown in Fig. \ref{fig:pipeline}): corners detection and document analysis. The formers takes as input a generic image containing a document and returns the 2D coordinates of its corners. The latter use the corners coordinates to warp the image, apply an OCR to read the document words and returns the original and warped image with the highlighted keywords specified by the user. Considering KODA as a black box, the user loads an image and, for each keyword specified, retrieves a copy of the image containing the highlighted word.

\begin{figure}[H]
	\includegraphics[width=\linewidth]{Pipeline.png}
	\caption{KODA Pipeline scheme with sub-tasks. The computationally expensive processing is done once per input image, then the user can search for keywords and retrieves the output image multiple times repeatedly.}
	\label{fig:pipeline}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{ipt.png}
	\caption{Image processing tasks example. Note: edges detection returns a resized (256x256)}
	\label{fig:imageprocessing}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=\linewidth]{canny_gaussian.png}
	\caption{Application of Canny edge detector to the original image without/with a Gaussian Filter}
	\label{fig:canny_gaussian}
\end{figure}

@@

\begin{figure}[htb!]
	\includegraphics[width=\linewidth]{canny_comparison.png}
	\caption{Comparison of different thresholds for Canny edge detector}
	\label{fig:canny_comparison}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{deep_edge_comparison.png}}%

@@

\section{Corners detection}

The corners detection task goal is to find the four document corners starting from the one-channel edges image. These points should be as precise as possible in order to define the tightest convex polygon around the document. The intuitive method to solve this task is to use the Hough transformation, as suggested in a Dropbox article \footnote{https://blogs.dropbox.com/tech/2016/08/fast-and-accurate-document-detection-for-scanning/}, to find straight lines that best approximate the document edges; the corners will be the intersection between those lines.

The suggested method, relies on finding more than one line per edge resulting in a set of intersections points. Those points are used to compute polygons and the one which best approximate the document edges is chosen to define the four corners. However, from empirical experiments, this could lead to an high amount of intersections meaning an enormous amount of polygons to test. Instead, KODA implementation extracts the best four lines ahead, so their intersections are immediately the best corners.

All the operations described in the following section are computed with reference to the resized edges image which is by default 256x256.

\subsection{Hough Transform}

OpenCV provides an interface for computing Hough lines \footnote{https://docs.opencv.org/2.4/doc/tutorials/imgproc/imgtrans/hough\_lines/hough\_lines.html} using polar coordinates (rho, theta); the problem is to calibrate the parameters and select the best lines retrieved. In order to remove unwanted noise in the edges image, an intensity threshold, which value was determined empirically (80), is applied before submitting it to the OpenCV interface. The threshold and the resolution interface parameters also were found empirically. The input images come from a natural environment with no control of lighting, so it can be expected that edges images intensity may heavily varies. For this reason, if no Hough lines are found, the task iteratively tries to reduce the threshold parameter by 10\% until enough lines are found or a maximum number of iterations is reached (default is 3).

Once a set of lines is found, a sub-task is responsible to select the four best ones, one per each document edge. This is accomplished exploiting the fact that the Hough lines returned by the OpenCV interface are ordered by confidence: the first four strongest ones are selected.

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{Hough.png}}
	\caption{TODO}
	\label{fig:hough}
\end{figure}

\subsection{Computing corners}

Once the four Hough lines corresponding to the document edges are found, computing the document corners means to correctly intersect the lines. They are ordered based on theta, so that parallel lines are near each other, then the intersections between alternated lines are computed. In particular, the intersection using polar is calculated as follow:

%TODO FORMULA

The implementation to find the intersection relies on \footnote{ numpy.linalg.solve: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.solve.html} which may raises an exception if the A matrix is singular because the computation is not possible. Whenever this happens, a least square solution, if it converges, via \footnote{numpy.linalg.lstsq: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.lstsq.html} is provided.

To maintain uniformity for the client APi, the corners are sorted following the Cartesian quadrants and they are scaled up based on the original image size provided as input.

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{computingcorners.png}}
	\caption{TODO}
	\label{fig:computingcorners}
\end{figure}

\section{Document analysis}

\subsection{Warping}

The first step of document analysis task is to warp the found paper within the image through a perspective transform using the detected corners. The document is expected to be A4 format, so the warped image size is computed considering the minimum of the possible widths (top, bottom) and heights (left, right), then forcing the greater dimension to be equals to the lesser one multiplied by the square root of 2 (ISO 216).

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{Warping.png}}
	\caption{TODO}
	\label{fig:warping}
\end{figure}

\subsection{OCR}

In order to implement the \textit{Optical Character Recognition} feature needed to highlight keywords, KODA uses \textit{Tesseract}[TODO REF], an open-source OCR engine by Google. Moreover, it uses \textit{TesserOCR}[TODO REF], a Python wrapper which provides a fast binding to the C++ native library and exposes all the low-level APIs.

TODO: talk about the iterator and put an image with bounding boxes

\subsection{Keyword highlighting}

The highlighting task goal is to apply a colored overlay on all the user specified keyword occurrences within the document in the image. Assuming the OCR library provides the bounding box of a detected word, a colored rectangle is drawn correspondingly on a image copy. The task output is the weighted sum of the original image and the overlay, resulting in a transparent highlighting effect on the keywords searched by the user.

The formula applied \footnote{https://docs.opencv.org/2.4/modules/core/doc/operations\_on\_arrays.html} is formally as follow: %

\begin{equation}
	out = src_1 \cdot \alpha + src_2 \cdot \beta + \gamma
\end{equation}

Where:

\begin{center}
	$src_1$ = overlay image \\
	$src_2$ = original image \\
	$\alpha$ = 0.3  \\
	$\beta$ = 1 - $\alpha$ \\
	$\gamma$ = 0 
\end{center}

However, the OCR library performs on the warped image, instead of the original one. For this reason, the overlay has to be warped back to the document shape as in the original image. This requirement is satisfied by applying a perspective transformation using the inverse of the perspective transform matrix used to find the warped image.

The KODA implementation (shown in Fig. \ref{fig:keywordhighliting}) relies on this concept, but actually transforms each bounding box instead of the entire final overlay. Transforming the warped image copy (final overlay) would leads to black pixels all over the areas the document is not present, so that adding to the original image results to darken areas outside the document. To maintain intact these areas, the highlights are drawn directly on the original image copy (not warped) after they are transformed correctly. Granted that further operations to avoid the darkened areas are possible, the KODA implementation was chosen because it does not introduce additional overhead.

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{kh.png}}
	\caption{Process to apply the highlight overlay.}
	\label{fig:keywordhighliting}
\end{figure}

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1.5\textwidth]{Highlighting.png}}
	\caption{ Examples of the keyword “on” highlighting. Note: the keyword is not searched as a perfect match, but as a substring of actual words. The highlight is applied to the entire word.}
	\label{fig:keywordhighliting2}
\end{figure}

\section{Conclusion}

TODO
